Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions

### 2023-05-03 presentation/index.qmd
create performance metrics for sequential models
prepare roc auc data
trying to figure out what to do with sensor problems. Calculate sleep stats accurately

tab_in_bed
```
:::

@@

## Lots of Metrics {transition="convex" .H2}

## {transition="convex"}
::: {layout="[[-1], [1], [-1]]"}
```{r}
source(here::here("presentation/code/tables_performance.R"))

tab_multi_metrics
```
:::

## {transition="convex" .H2}

::: {layout="[[-1], [1], [-1]]"}
```{r}
tab_crude_metrics
```
:::

## {transition="convex" .H2}

```{r}
tab_br_metrics
```

>>>>

table_in_bed_metrics
```
:::

@@

## Roc curves for sleep models {transition="convex}
:::: {.columns}

::: {.column width="60%"}
![](visuals/plot_sleep_roc.png)
:::

::: {.column width="40%"}
```{r}
source(here::here("presentation/code/table_roc_auc_sleep.R"))

gt::as_raw_html(table_sleep_roc_auc)
```
:::

## {transition="convex"}

```{r}
table_sleep_metrics
```
